`Total-evidence' Bayesian estimation of phylogeny, divergence times and fossil ages

### 2015-11-02 totalEvidenceTalk/pics/SampledTree2.tex
reorganize to separate talk and paper

\pause

%sampled nodes
\node[fill,circle, inner sep=2pt] at (-2.5, 1)(sA){};
\node[anchor=north] (Alet) at (sA) {\textcolor{black}{\footnotesize A}};
\node[fill,circle, inner sep=2pt] at (0, 1)(sB){};
\node[anchor=north] (Alet) at (sB) {\textcolor{black}{\footnotesize B}};
\node[fill,circle, inner sep=2pt] at (2, 1)(sC){};
\node[anchor=north] (Alet) at (sC) {\textcolor{black}{\footnotesize C}};
\node[fill,circle, inner sep=2pt] at (3.2, 1)(sD){};
\node[anchor=north] (Alet) at (sD) {\textcolor{black}{\footnotesize D}};

\pause

\node[fill,circle, inner sep=2pt] at (3.3, 5)(sE){};
\node[anchor=west] (Alet) at (sE) {\textcolor{black}{\footnotesize E}};
\node[fill,circle, inner sep=2pt] at (-1, 2.9)(sF){};
\node[anchor=west] (Alet) at (sF) {\textcolor{black}{\footnotesize F}};

\pause

@@

%sampled nodes
\node[fill,circle, inner sep=2pt] at (-2.5, 1)(sA){};
\node[anchor=north] (Alet) at (sA) {\textcolor{black}{\footnotesize A}};
\node[fill,circle, inner sep=2pt] at (0, 1)(sB){};
\node[anchor=north] (Alet) at (sB) {\textcolor{black}{\footnotesize B}};
\node[fill,circle, inner sep=2pt] at (2, 1)(sC){};
\node[anchor=north] (Alet) at (sC) {\textcolor{black}{\footnotesize C}};
\node[fill,circle, inner sep=2pt] at (3.2, 1)(sD){};
\node[anchor=north] (Alet) at (sD) {\textcolor{black}{\footnotesize D}};

\node[fill,circle, inner sep=2pt] at (3.3, 5)(sE){};
\node[anchor=west] (Alet) at (sE) {\textcolor{black}{\footnotesize E}};
\node[fill,circle, inner sep=2pt] at (-1, 2.9)(sF){};
\node[anchor=west] (Alet) at (sF) {\textcolor{black}{\footnotesize F}};

@@

\color{white}

%terminal nodes
\node[fill,circle, inner sep=2pt] at (-3, 1)(sA){};
\node[anchor=north] (Alet) at (sA) {\textcolor{white}{\footnotesize A}};
\node[fill,circle, inner sep=2pt] at (0.7, 1)(sB){};
\node[anchor=north] (Alet) at (sB) {\textcolor{white}{\footnotesize B}};
\node[fill,circle, inner sep=2pt] at (2.7, 1)(sC){};
\node[anchor=north] (Alet) at (sC) {\textcolor{white}{\footnotesize C}};
\node[fill,circle, inner sep=2pt] at (3.9, 1)(sD){};
\node[anchor=north] (Alet) at (sD) {\textcolor{white}{\footnotesize D}};
\node[fill,circle, inner sep=2pt] at (-1, 2.9)(sF){};
\node[anchor=west] (Alet) at (sF) {\textcolor{white}{\footnotesize F}};
\node[fill,circle, inner sep=2pt] at (3.3, 5)(sE){};
\node[anchor=west] (Alet) at (sE) {\textcolor{white}{\footnotesize E}};

%branches
\draw (0, 7.5) -- (0,7) -- (-2, 7) --(-2, 5.5) --(-3, 5.5)  -- (sA);
\draw (-2, 5.5) -- (-1, 5.5) -- (sF); 
\draw (0,7) -- (2,7) -- (2,5.8) -- (0.7, 5.8) -- (0.7, 4.5) -- (sB); 
\draw (2, 5.8) -- (3.3, 5.8) -- (3.3, 4) -- (3.3, 2.1) -- (2.7, 2.1) -- (sC); 
\draw (3.3, 2.1) -- (3.9, 2.1) -- (sD);

>>>>

%sampled nodes
\node[fill,circle, inner sep=2pt] at (-2.5, 1)(sA){};
\node[anchor=north] (Alet) at (sA) {\textcolor{black}{\footnotesize A}};
\node[fill,circle, inner sep=2pt] at (0, 1)(sB){};
\node[anchor=north] (Alet) at (sB) {\textcolor{black}{\footnotesize B}};
\node[fill,circle, inner sep=2pt] at (2, 1)(sC){};
\node[anchor=north] (Alet) at (sC) {\textcolor{black}{\footnotesize C}};
\node[fill,circle, inner sep=2pt] at (3.2, 1)(sD){};
\node[anchor=north] (Alet) at (sD) {\textcolor{black}{\footnotesize D}};
\node[fill,circle, inner sep=2pt] at (3.3, 5)(sE){};
\node[anchor=west] (Alet) at (sE) {\textcolor{black}{\footnotesize E}};
\node[fill,circle, inner sep=2pt] at (-1, 2.9)(sF){};
\node[anchor=west] (Alet) at (sF) {\textcolor{black}{\footnotesize F}};

@@

%sampled nodes
\node[fill,circle, inner sep=2pt] at (-2.5, 1)(sA){};
\node[anchor=north] (Alet) at (sA) {\textcolor{black}{\footnotesize A}};
\node[fill,circle, inner sep=2pt] at (0, 1)(sB){};
\node[anchor=north] (Alet) at (sB) {\textcolor{black}{\footnotesize B}};
\node[fill,circle, inner sep=2pt] at (2, 1)(sC){};
\node[anchor=north] (Alet) at (sC) {\textcolor{black}{\footnotesize C}};
\node[fill,circle, inner sep=2pt] at (3.2, 1)(sD){};
\node[anchor=north] (Alet) at (sD) {\textcolor{black}{\footnotesize D}};
\node[fill,circle, inner sep=2pt] at (3.3, 5)(sE){};
\node[anchor=west] (Alet) at (sE) {\textcolor{black}{\footnotesize E}};
\node[fill,circle, inner sep=2pt] at (-1, 2.9)(sF){};
\node[anchor=west] (Alet) at (sF) {\textcolor{black}{\footnotesize F}};

@@

%terminal nodes
\node[fill,circle, inner sep=2pt] at (-3, 1)(sA){};
\node[anchor=north] (Alet) at (sA) {\textcolor{black}{\footnotesize A}};
\node[fill,circle, inner sep=2pt] at (0.7, 1)(sB){};
\node[anchor=north] (Alet) at (sB) {\textcolor{black}{\footnotesize B}};
\node[fill,circle, inner sep=2pt] at (2.7, 1)(sC){};
\node[anchor=north] (Alet) at (sC) {\textcolor{black}{\footnotesize C}};
\node[fill,circle, inner sep=2pt] at (3.9, 1)(sD){};
\node[anchor=north] (Alet) at (sD) {\textcolor{black}{\footnotesize D}};
\node[fill,circle, inner sep=2pt] at (-1, 2.9)(sF){};
\node[anchor=west] (Alet) at (sF) {\textcolor{black}{\footnotesize F}};
\node[fill,circle, inner sep=2pt] at (3.3, 5)(sE){};
\node[anchor=west] (Alet) at (sE) {\textcolor{black}{\footnotesize E}};

%branches

\draw (0, 7.5) -- (0,7) -- (-2, 7) --(-2, 5.5) --(-3, 5.5)  -- (sA);
\draw (-2, 5.5) -- (-1, 5.5) -- (sF); 
\draw (0,7) -- (2,7) -- (2,5.8) -- (0.7, 5.8) -- (0.7, 4.5) -- (sB); 
\draw (2, 5.8) -- (3.3, 5.8) -- (3.3, 4) -- (3.3, 2.1) -- (2.7, 2.1) -- (sC); 
\draw (3.3, 2.1) -- (3.9, 2.1) -- (sD);

\node at (0.6, -1) {\textcolor{newblue1}{Sampled tree}};
